Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-3\baselineskip}

### 2017-03-15 paper/ms.tex
words about rotation example

To demonstrate this model, we

\rotationperiod

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=\textwidth]{figures/rotation.pdf}
\caption{Inferred constraints on a quasiperiodic GP model using the covariance
    function in \eq{rot-kernel} and one quarter of \kepler\ data.
(left) The \kepler\ data (black points) and the maximum likelihood model
    prediction (blue curve).
    The solid blue line shows the predictive mean and the blue contours show
    the predictive standard deviation.
(center) Inferred constraints on the model PSD.
    The dashed line shows the maximum likelihood PSD, the blue solid line
    shows the median of posterior PSD, and the blue contours show the 68\%
    credible region.
(right) Inferred constraints on the model covariance function from
    \eq{rot-kernel}.
    The dashed line shows the maximum likelihood model, the blue solid line
    shows the median of posterior, and the blue contours show the 68\%
    credible region.
    \figurelabel{rotation}}
\end{center}
\end{figure}

>>>>

To demonstrate this model, we fit a \celerite\ model with a kernel given by
\eq{rot-kernel} to a \kepler\ light curve for the star KIC~1430163.
This star has a published rotation period of $3.88 \pm 0.58$ measured using
traditional periodogram and autocorrelation function approaches applied to
\kepler\ data from Quarters 0--16 \citep{Mathur:2014}.
We used \emcee\ to sample to posterior probability density for the four
parameters in \eq{rot-kernel} conditioned on two quarters of \kepler\ data and
find a constraint on the rotation period of $P = \rotationperiod$ in good
agreement with the literature value.
\Figure{rotation} shows a subset of the data used in this example and the
posterior inferences of the PSD and autocorrelation function of the process.
\Figure{rotation-period} shows the marginalized posterior distribution for the
rotation period.

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=\textwidth]{figures/rotation.pdf}
\caption{Inferred constraints on a quasiperiodic GP model using the covariance
    function in \eq{rot-kernel} and two quarters of \kepler\ data.
(left) The \kepler\ data (black points) and the maximum likelihood model
    prediction (blue curve) for a 50~day subset of the data used.
    The solid blue line shows the predictive mean and the blue contours show
    the predictive standard deviation.
(center) Inferred constraints on the model PSD.
    The dashed line shows the maximum likelihood PSD, the blue solid line
    shows the median of posterior PSD, and the blue contours show the 68\%
    credible region.
(right) Inferred constraints on the model covariance function from
    \eq{rot-kernel}.
    The dashed line shows the maximum likelihood model, the blue solid line
    shows the median of posterior, and the blue contours show the 68\%
    credible region.
    \figurelabel{rotation}}
\end{center}
\end{figure}
